\newpage
\section*{\centering{\songti{攻读博士学位期间发表论文和科研情况}}}
%\vskip 5mm
{\heiti $\blacksquare$ 已公开发表论文}\vskip 5mm

\begin{enumerate}
	
	\item Ye Li, Fan Xia, \textbf{Chengcheng Yu}, Weining Qian, and Aoying Zhou. Sampling social streams for hot social events analytics. In 31st IEEE International Conference on Data Engineering Workshops (ICDEW), 2015, pp. 198-201. IEEE, 2015.

	\item \textbf{Chengcheng Yu}, Fan Xia, Weining Qian, Aoying Zhou, and Jianlong Chang. On efficiently generating realistic social media timeline structures. In Proceedings of the 26th International Conference on Scientific and Statistical Database Management, p. 45. ACM, 2014.
	
	\item \textbf{Chengcheng Yu}, Fan Xia, Qunyan Zhang, Haixin Ma, Weining Qian, Minqi Zhou, Cheqing Jin, and Aoying Zhou. BSMA-Gen: a parallel synthetic data generator for social media timeline structures. In Database Systems for Advanced Applications, pp. 539-542. Springer, 2014.
	
	\item Fan Xia, Ye Li, \textbf{Chengcheng Yu}, Haixin Ma, and Weining Qian. BSMA: A benchmark for analytical queries over social media data. In Proceedings of the VLDB Endowment 7, no. 13 (2014): 1573-1576.
	
	
	\item Li Wang, Lei Zhang, \textbf{Chengcheng Yu}, Aoying Zhou. Optimizing Pipelined Execution for Distributed In-memory OLAY System. In Database Systems for Advanced Applications Workshop, pp. 35-56. Springer, 2014.
	
	\item Haixin Ma, Jinxian Wei, Weining Qian, \textbf{Chengcheng Yu}, Fan Xia, and Aoying Zhou. Optimizing Pipelined Execution for Distributed In-Memory OLAP System. In First International Workshop on Graph Data Management Experiences and Systems, p. 10. ACM, 2013.
	

	
	
\end{enumerate}

%\bigskip\bigskip\bigskip
\bigskip
{\heiti $\blacksquare$ 尚未发表论文}\vskip 5mm
\begin{spacing}{1.2}
\begin{enumerate}
	\item 
\end{enumerate}
\end{spacing}
%{\heiti $\blacksquare$ 攻读学位期间参加的科研项目}\vskip 5mm
%\vskip 3mm
