\chapter*{\centering{\songti{攻读博士学位期间发表的学术论文、科研情况以及奖项}}}
%\vskip 5mm
{\heiti $\blacksquare$ 已公开发表论文}
	\vskip 5mm

\begin{enumerate}
	\renewcommand{\labelenumi}{[\theenumi]}
	\renewcommand\baselinestretch{1}\selectfont 	
	
	\item  \textbf{Keqiang Wang}, Wayne Xin Zhao, Hongwei Peng, Xiaoling Wang. Bayesian Probabilistic Multi-Topic Matrix Factorization for Rating Prediction. In \textit{Proceedings of the 25th International Joint Conference on Artificial Intelligence} (IJCAI), pages 3910-3916, 2016.
	
	\item \textbf{Keqiang Wang}, Hongwei Peng, Yuanyuan jin, Chanfeng Sha, Xiaoling Wang. Local Weighted Matrix Factorization for Top-n Recommendation with Implicit Feedback. In \textit{Data Science and Engineering} (DSE), volume 1, no. 4, pages 252-264, 2016.
	
	\item \textbf{Keqiang Wang}, Xiaoyi Duan, Jiansong Ma, Chaofeng Sha, Xiaoling Wang, Aoying Zhou. Local Weighted Matrix Factorization for Implicit Feedback Datasets. In Proceedings of \textit{the 21th Database Systems for Advanced Applications} (DASFAA), pages 381-395, 2016.
	
	\item \textbf{Keqiang Wang}, Chaofeng Sha, Xiaoling Wang, Aoying Zhou. Based on Citation Diversity to Explore Influential Papers for Interdisciplinarity. In \textit{Proceedings of the 16th Asia-Pacific Web Conference} (APWeb), pages 343-354, 2014. (Best Student Paper)
	
	\item Chaofeng Sha, \textbf{Keqiang Wang}, Xiaoling Wang, Aoying Zhou. Optimizing Top-k Retrieval: Submodularity Analysis and Search Strategies. In \textit{Frontiers of Computer Science} (FCS), volume 10, no. 3, pages 477-487, 2016.
	
	\item 马建松, \textbf{王科强}, 宋光旋, 张凯, 王晓玲, 金澈清. 面向 MAX/MIN 优化的 SQL Window 函数处理. \textit{计算机学报}, 39卷, 10期, 2149-2160页, 2016.
	
	\item Kai Zhang, \textbf{Keqiang Wang}, Xiaoling Wang, Aoying Zhou. Hotel recommendation based on user preference analysis. In \textit{Proceeding of the 31th IEEE International Conference on Data Engineering Workshops} (ICDEW), pages 134-138, 2015.
	
	\item Chaofeng Sha, \textbf{Keqiang Wang}, Dell Zhang, Xiaoling Wang, Aoying Zhou. Optimizing Top-k Retrieval: Submodularity Analysis and Search Strategies. In Proceedings of \textit{the 15th International Conference on Web-Age Information Management} (WAIM), pages 18-29, 2014.
	
	\item Chaofeng Sha, \textbf{Keqiang Wang}, Xiaoling Wang, Aoying Zhou. Ensemble Pruning: A Submodular Function Maximization Perspective.  In Proceedings of \textit{the 19th Database Systems for Advanced Applications} (DASFAA), pages 1-15, 2014.
	
	\item Chaofeng Sha, \textbf{Keqiang Wang}, Kai Zhang, Xiaoling Wang, Aoying Zhou. Diversifying Top-k Service Retrieval. In Proceeedings of \textit{the 11th IEEE International Conference on Services Computing} (SCC), pages 227-234, 2014.
	
	\item 张凯, \textbf{王科强}, 王晓玲, 金澈清, 周傲英. 基于评论分析的酒店推荐系统. 计算机研究与发展, 增刊I, 51卷, 372-376页, 2014.

	\item Hongwei Peng, Haojie Hu, \textbf{Keqiang Wang}, Xiaoling Wang.
	Time-Aware and Topic-Based Reviewer Assignment.  In Proceedings of \textit{the 22th Database Systems for Advanced Applications Workshops} (DASFAA Workshops), pages 145-157, 2017.
\end{enumerate}

{\heiti $\blacksquare$ 参加的科研项目}
\begin{enumerate}
	\renewcommand{\labelenumi}{[\theenumi]}
	\renewcommand\baselinestretch{1}\selectfont 	
	
	\item 海量众包数据管理的关键技术（国家自然科学基金面上项目，编号：61472141）
	
	\item XML 个性化协作搜索及其在社会网络服务中的应用（国家自然科学基金面上项目，编号：61170085）
	
	\item 数据密集型计算环境下的数据管理方法与技术（国家自然科学基金面上项目，编号：61033007）
	
	\item 海量音频数据管理系统，核高基项目《非结构化数据管理系统》（编号：2010ZX01042-002-003-004）

\end{enumerate}
{\heiti $\blacksquare$ 获得奖项}
\begin{enumerate}
	\renewcommand{\labelenumi}{[\theenumi]}
	\renewcommand\baselinestretch{1}\selectfont 	
	\item 上海市优秀毕业生，2017
	\item  研究生国家奖学金，2016
	\item 校优秀学生，2016
	\item 智慧研究生奖学金，2015
	\item CCF 数据竞赛三等奖，2014
\end{enumerate}